An Automatic Verification Framework for Software Configurations

### 2016-05-08 OSDI/motiv.tex
hyphens
better motiv

In this section, we present several {\em tricky} configuration errors
extracted from real-world examples. 
The reason we call them tricky is
most of existing efforts, \eg, learning-based checking
efforts~\cite{zhang14encore, wang04automatic}, cannot detect
these configuration errors.
On the other hand, we also investigated 
many misconfiguration problems in practice were caused by 
these tricky configuration errors, \eg, reported by Stack Overflow.

@@

This user complained his MySQL's load is very high and the website's
respond speed is very slow.
In this case, {\tt key\_buffer\_size} is used by all the threads
cooperatively while {\tt join\_buffer} and {\tt sort\_buffer} are 
created by each thread for private use; thus, the maximum amount
of used key buffer, \ie, {\tt key\_buffer\_size} should be larger than 
{\tt join|sort\_buffer\_size} * {\tt max\_connections}. 
Clearly, in the above example, it does not hold, 
so that this misconfiguration causes MySQL loads very slow.

@@

\para{Other errors.}
\app can also deal with the configuration errors that can be detected by
existing work, such as EnCore~\cite{zhang14encore} and
CODE~\cite{yuan11context}.
For a configuration error reported recently made MySQL
daemon failed to start~\cite{syserror}.
One entry in a MySQL configuration file is written as 
{\tt datadir=/root/appfinder/mysql}, and the type as well as 
format seem to be correct.
However, the problem is this directory should not be
initiated as a root directory, and the correct entry
should be {\tt datadir=/appfinder/mysql}.
Such an error is called system environment related configuration error.
Both \app and EnCore can handle system execution related
misconfiguration problems.
Furthermore, \app is also able to detect type errors and syntax errors
in configuration files.

>>>>

In this section, we present several {\em tricky} configuration errors
extracted from real-world examples. 
The reason we call them tricky is that
most of existing efforts, \eg, learning-based checking
efforts~\cite{zhang14encore, wang04automatic}, cannot detect
these configuration errors.
On the other hand, we also investigated 
many misconfiguration problems in practice which were caused by 
these tricky configuration errors, \eg, reported by Stack Overflow.

@@

This user complained that his MySQL's load was very high and the website's
respond speed was very slow.
In this case, {\tt key\_buffer\_size} is used by all the threads
cooperatively while {\tt join\_buffer} and {\tt sort\_buffer} are 
created by each thread for private use; thus, the maximum amount
of used key buffer, \ie, {\tt key\_buffer\_size} should be larger than 
{\tt join|sort\_buffer\_size} * {\tt max\_connections}. 
Clearly, in the above example, it does not hold, 
so that this misconfiguration causes MySQL loads very slow.

@@

\para{Other errors.}
\app can also deal with the configuration errors that can be detected by
existing work, such as EnCore~\cite{zhang14encore} and
CODE~\cite{yuan11context}.
For a configuration error reported recently made MySQL
daemon failed to start~\cite{syserror}.
One entry in a MySQL configuration file is written as 
{\tt datadir=/root/appfinder/mysql}, and the type as well as 
format seem to be correct.
However, the problem is this directory should not be
initiated as a root directory, and the correct entry
should be {\tt datadir=/appfinder/mysql}.
Such an error is called system environment-related configuration error.
Both \app and EnCore can handle system execution related
misconfiguration problems.
Furthermore, \app is also able to detect type errors and syntax errors
in configuration files.
